Prefetching SPARQL query cacher

### 2016-05-12 dissertation/cache-proxy.tex
LDF client

>>>>

The Linked Data Fragment client work was started prior to this project
by Patrick Hochstenbach, and consists of the client code for Triple
Pattern Fragments in \pmodule{RDF::LDF}. It also includes the Basic
Graph Pattern optimisation from \ref{ldf2}. Included with the client
code is an implementation of a triple store of the legacy
\pmodule{RDF::Trine} framework that predates Attean. He also started
an Attean store implementation \pmodule{AtteanX::Store::LDF}, but that
module was subsequently adopted by me, and I have written most of the
functionality. It composes the TripleStore API and implements triple
pattern queries and cardinality estimates, both provided by the
underlying client code as they are a part of the core functionality of
Triple Pattern Fragments, but also a \pcode{cost\_for\_plan}
implementation used by the cost planner.
